\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-09 Paper_honeypot.tex
wat aanpassingen

These 404's are interesting because they show us what adresses the attackers were trying to access. For instance, we see a lot of scans for phpMyAdmin (phpMyAdmin-3.3.10.5, phpMyAdmin-3.4.7, phpMyAdmin-3.4.6 etcetera). They also searched non existing folders for these phpMyAdmin files.

Also serveral client IDs are visible in these logs: "\verbatim{"-"}", which is a blank user/client ID, (3432 attempts), "MiRRORS" (310 attempts), "ZmEu" (41 attempts) and "Morfeus Fucking Scanner" (4 attempts). These seem to be search engine crawlers. It is interesting to see that both several "\verbatim{"-"}" and several "ZmEu" users are scanning for "/w00tw00t.at.blackhats.romanian.anti-sec:)" and "/w00tw00t.at.ISC.SANS.DFind:)". The attackers using "ZmEu" found one valid path: /phpmyadmin/, however he did not exploit this. "Morfeus Fucking Scanner" was used by one attacker, that soly searched for /user/soapCaller.bs. We could not find anything on this .bs file. We expected to see several occurances of "/robots.txt" because this is a common way to start when using a search engine crawler, but none were found.

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Connection} we can conclude that...

Our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.

Concluding:

@@

>>>>

These 404's are interesting because they show us what adresses the attackers were trying to access. For instance, we see a lot of scans for phpMyAdmin (phpMyAdmin-3.3.10.5, phpMyAdmin-3.4.7, phpMyAdmin-3.4.6 etcetera). They also searched non existing folders for these phpMyAdmin files. Also serveral client IDs are visible in these logs: "\verbatim{"-"}", which is a blank user/client ID, (3432 attempts), "MiRRORS" (310 attempts), "ZmEu" (41 attempts) and "Morfeus Fucking Scanner" (4 attempts). These seem to be search engine crawlers. It is interesting to see that both several "\verbatim{"-"}" and several "ZmEu" users are scanning for "/w00tw00t.at.blackhats.romanian.anti-sec:)" and "/w00tw00t.at.ISC.SANS.DFind:)". The attackers using "ZmEu" found one valid path: /phpmyadmin/, however he did not exploit this. Morfeus Fucking Scanner was used by one attacker, that soly searched for /user/soapCaller.bs. We could not find anything on this .bs file. We expected to see several occurances of "/robots.txt" because this is a common way to start when using a search engine crawler, but none were found.

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Connection} we can conclude that our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.

@@

\begin{itemize}
\item Low/High interaction phase
\item GHH
\item etc
\end{itemize}
